### 2017-06-05 Hhh/Hhh.tex
Corrections

In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of tau leptons, is discussed. In this analysis, which 
uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the di-tau pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
For these results I contributed to the analysis of the \etau and \mutau channels,
and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 p-p 
running period of the LHC. 
Signal and background events are generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator is used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
are used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

@@

To better model the \Ztautau background an embedding technique is used. In this method, 
\Zmm events are selected in data and the muons are replaced by simulated taus. \texttt{TAUOLA} is used
to decay the taus, with the final state particles passed through the detector simulation. %and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. 
Tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originating from the \PZ boson have been removed. This technique is also applied to 
a simulated \ttbar sample to estimate the \ttbar contamination in the \Zmm embedded sample. %This contribution
%needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
%avoid double counting with the \ttbar \ac{MC}.

@@

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least $20\,\GeV$ and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the transverse and longitudinal impact parameters with respect to the primary vertex, $d_{xy}$ and $d_{z}$, must be smaller
than $0.045\,\cm$ and $0.2\,\cm$ respectively. Tight muon identification
criteria and a tight isolation requirement, $I_{\text{rel}}^{\mu} < 0.1$,
 are applied. The hadronic tau must have a \pT~of at least
$20\,\GeV$, $|\eta| < 2.3$, and must have $d_{z} < 0.2\,\cm$. It is required to pass 
the decay mode finding identification
from the HPS algorithm. Additionally,
the combined isolation is required to be
at most $1.5\,\GeV$. To reject $\Pe/\Pgm \rightarrow$ \Pgth fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-muon discriminator
and the loose working point of the cut-based anti-electron discriminator.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_mt_2012.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_et_2012.pdf}}
\end{center}
\caption[\mT~distributions in the \mutau and \etau channels.]{\mT~distributions in the (a) \mutau and (b) \etau channels.}
\label{fig:Hhh_selection_mt}
\end{figure}

@@

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), \mbox{2jet-1tag} 
(at least two jets, exactly one of which is b-tagged), \mbox{2jet-2tag} (at least two jets, at least two of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, and the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
channels, illustrates this.

@@

In a kinematic fit constraints are made on the event kinematics, in the
case of this analysis these constraints are
$m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
$m(\Pbottom_{1},\Pbottom_{2}) = m_{\PHiggslight} = 125\,\GeV$.
The kinematic observables related to the hadronic taus and jets
are varied within their uncertainties to fulfil these 
constraints. A $\chi^2$ cost term is introduced for each
observable that is varied with respect to the measurement;
the aim of the fit is to minimise the sum of these $\chi^2$ terms.

For b-jets, the reconstructed direction in $\eta$ and $\phi$ is 
assumed to be measured accurately in comparison with their energy.
Therefore only their energy is varied in the fit. In addition, we assume
that uncertainties in the energy measurement directly translate to
uncertainties in the momentum measurement, and therefore $\vec{\beta} = \vec{p}/E$ is
also kept constant.

Before the fit, the mass constraint gives:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_prefit}
m_{\PHiggslight}^2 &= E_{\PHiggslight}^2 - \vec{p_{\PHiggslight}}^2 = (E_{\Pbottom 1}+E_{\Pbottom 2})^2 - (\vec{p_{\Pbottom 1}} + \vec{p_{\Pbottom 2}})^2 \notag\\
& = 2E_{\Pbottom 1}E_{\Pbottom 2} + m_{\Pbottom 1}^2 +m_{\Pbottom 2}^2 - 2\vec{p_{\Pbottom 1}}\vec{p_{\Pbottom 2}} \notag\\
& = m_{\Pbottom 1}^2 +m_{\Pbottom 2}^2 - 2E_{\Pbottom 1}E_{\Pbottom 2}(1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})\notag\\
&\Rightarrow (1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}}) = \frac{m_{\PHiggslight}^2 - m_{\Pbottom 1}^2 - m_{\Pbottom 2}^2}{2E_{\Pbottom 1}E_{\Pbottom 2}}.
\end{align}
When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})$ 
and
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:gamma_def}
\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2},
\end{equation}
we get:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_variation}
m_{\PHiggslight}^2 &= m_{\Pbottom 1}^2 + m_{\Pbottom 2}^2 - 2E_{\Pbottom 1}E_{\Pbottom 2}(1-\vec{\beta_{\Pbottom 1}}\vec{\beta_{\Pbottom 2}})\notag\\
&= m_{\Pbottom 1}^2 +\frac{E_{\Pbottom 2,\text{fit}}^2}{\gamma_{\Pbottom 2}^2} +2\mathcal{A}E_{\Pbottom 1}E_{\Pbottom 2,\text{fit}}\notag\\
\Rightarrow E_{\Pbottom 2}^{\text{fit}}& = \frac{(-2E_{\Pbottom 1}\mathcal{A} + \sqrt{4E_{\Pbottom 1}^2\mathcal{A} - 4(m_{\Pbottom 1}^2-m_{\PHiggslight}^2)\gamma_{\Pbottom 2}^{-2}})\gamma_{\Pbottom 2}^2}{2}\notag\\
&= - E_{\Pbottom 1}\mathcal{A}\gamma_{\Pbottom 2}^2+\sqrt{E_{\Pbottom 1}^2\mathcal{A}\gamma_{\Pbottom 2}^4 - (m_{\Pbottom 1}^2 - m_{\PHiggslight}^2)\gamma_{\Pbottom 2}^2}\notag\\
&\Rightarrow E_{\Pbottom 2}^{\text{fit}} = E_{\Pbottom 1}\mathcal{A}\gamma_{\Pbottom 2}^2(-1 + \sqrt{1+\frac{m_{\PHiggslight}^2 - m_{\Pbottom 1}^2}{E_{\Pbottom 1}^2\mathcal{A}\gamma_{\Pbottom 2}^2}}).
\end{align}

The fitting procedure additionally modifies the masses of the b-jets as 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{\Pbottom_{1,2}}^{\text{fit}} = m_{\Pbottom{1,2}}\frac{E_{\Pbottom{1,2}}^{\text{fit}}}{E_{\Pbottom{1,2}}}.
\end{equation}
The $\chi^2$ term for each b-jet is calculated as $\chi_{\Pbottom 1,2}^2 = \frac{E_{\Pbottom 1,2}^{\text{fit}}-E_{\Pbottom 1,2}^{\text{meas}}}{\sigma_{\Pbottom 1,2}}$, where `meas' denotes the measured value and `fit' the value given by the fit.

For taus only the visible decay products are measured. Assuming these point in 
the same direction as the original tau, a similar procedure as for the b-jets can be employed to constrain the energy of the second tau
when varying the energy of the first tau in the fit. The masses of the taus are kept fixed at $m_{\Pgt}$ throughout the procedure.

@@

The measured recoil is 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p}_{\text{T,recoil}}^{\text{ meas}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ meas}} = -\vec{p}_{\text{T,miss}}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 1}^{\text{ meas}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_1^{\text{vis}}}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_2^{\text{vis}}}^{\text{ meas}},
\end{equation}
and the recoil from the fit is,
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p}_{\text{T,recoil}}^{\text{ fit}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ fit}} = - \vec{p}_{\text{T},\Pbottom 1}^{\text{ fit}} - \vec{p}_{\text{T},\Pbottom 2}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_1}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_2}^{\text{ fit}}.
\end{equation}
A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}})^T V_{\text{recoil}}^{-1}(\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}}),
\end{equation}
where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as 
\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p}_{\text{T,miss}}} - V_{\Pbottom {1}} - V_{\Pbottom 2},
\end{equation}
 from the covariance matrices of the b-jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET,
while the covariance matrices of the b-jets can be written in terms of the position, momentum and resolution of the b-jets. 
The total $\chi^2$ term that needs to be minimised in the fit can then be written as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{\Pbottom 1} + \chi^2_{\Pbottom 2} + \chi^2_{\text{recoil}}.
\end{equation}
The results of the kinematic fit are the tau and b-jet four-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.

As illustrated in figure \ref{fig:kinfitvsmjj}a the use of the kinematic fit greatly
improves the resolution of the reconstructed heavy Higgs boson mass in signal events, when 
compared with the simple four-body mass reconstruction. It also shifts the mean of the
distribution closer to the true value. It is also insightful to make such a comparison
for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between four-body mass and
kinematic fit mass for \ttbar events is shown in figure 
\ref{fig:kinfitvsmjj}b. This figure shows that the mass distribution for
background events is less affected by the kinematic fit, although due to the
invariant mass constraint the minimum of the reconstructed mass distribution
is forced to $250\,\GeV$.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. The yield of
\Ztautau in each category is evaluated in two steps. In the first
step the total yield after the initial event selection, before subdividing into categories,
is evaluated in the simulated \Ztautau sample. In the second step the yield obtained 
in the first step is scaled by the efficiency with which such events pass the 
category selection in the embedded sample.
The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using simulation.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to \mbox{low-\mT}~extrapolation
 factor is determined from the \Wjets simulation.
The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

@@

The shapes in all categories are taken from same-sign data with the electron or muon
isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
inverting the light lepton isolation requirements, the category definition
is relaxed to obtain the shapes. For the purposes of QCD shape
estimation, jets are considered b-tagged if they pass the loose b-tagging
working point.
\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shapes and normalisations are
estimated using simulated samples.

@@

shape of its kinematic fit mass distribution. 

@@

fake rate correction is close to 1, which is why it is not applied, but the uncertainty is 

@@

\item \ttbar: The uncertainty in the \ttbar cross section is 10\% \cite{toppp}.

>>>>

In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of tau leptons, is discussed. In this analysis, which 
uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the di-tau pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
For these results I contributed to the analysis of the \etau and \mutau channels, studying alternative \ttbar
background rejection methods and other uses of the kinmeatic fit variable which are not further discussed.
My main contribution was the statistical inference for the \Htohh analysis, which included limit setting and performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 p-p 
running period of the LHC. 
Signal and background events are generated using several different \ac{MC} event generators. With the exception
of the embedded samples described later in this section, all of these simulated
samples are centrally produced for use by all CMS analyses. The \texttt{MadGraph}
\cite{madgraph} matrix element generator is used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
are used for the \Wjets and \Zellell backgrounds. This increases the number of simulated background events
in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

@@

To better model the \Ztautau background an embedding technique is used \cite{SMHtautauCMS}. In this method, 
\Zmm events are selected in data and the muons are replaced by simulated taus. \texttt{TAUOLA} is used
to decay the taus, with the final state particles passed through the detector simulation. %and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. 
Tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originating from the \PZ boson have been removed. This technique is also applied to 
a simulated \ttbar sample to estimate the \ttbar contamination in the \Zmm embedded sample. %This contribution
%needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
%avoid double counting with the \ttbar \ac{MC}.

@@

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least $20\,\GeV$ and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the transverse and longitudinal impact parameters with respect to the primary vertex, $d_{xy}$ and $d_{z}$, must be smaller
than $0.045\,\cm$ and $0.2\,\cm$ respectively. Tight muon identification
criteria and a tight isolation requirement, $I_{\text{rel}}^{\mu} < 0.1$,
 are applied. The hadronic tau must have a \pT~of at least
$20\,\GeV$, $|\eta| < 2.3$, and must have $d_{z} < 0.2\,\cm$. It is required to pass 
the decay mode finding identification
from the HPS algorithm. Additionally,
the isolation sum (equation \ref{eqn:cutbased_iso}) is required to be
at most $1.5\,\GeV$. To reject $\Pe/\Pgm \rightarrow$ \Pgth fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-muon discriminator
and the loose working point of the cut-based anti-electron discriminator.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_mt_2012_corrs.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_et_2012_corrs.pdf}}
\end{center}
\caption[\mT~distributions in the \mutau and \etau channels.]{\mT~distributions in the (a) \mutau and (b) \etau channels. The signal
at \mH~$=300\,\GeV$ and \tanb~$=2$ in the \ac{MSSM} low-\tanb~scenario, multiplied by a factor of 100, is overlaid.}
\label{fig:Hhh_selection_mt}
\end{figure}

@@

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), \mbox{2jet-1tag} 
(at least two jets, exactly one of which is b-tagged), \mbox{2jet-2tag} (at least two jets, at least two of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator. The
typical b-tagging efficiency at this working point is 70\% \cite{BTV8TeV}.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, and the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
channels, illustrates this.

@@

In a kinematic fit constraints are made on the event kinematics, in the
case of this analysis these constraints are
$m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
$m(\text{j}_{1},\text{j}_{2}) = m_{\PHiggslight} = 125\,\GeV$.
The kinematic observables related to the hadronic taus and jets
are varied within their uncertainties to fulfil these 
constraints. A $\chi^2$ cost term is introduced for each
observable that is varied with respect to the measurement;
the aim of the fit is to minimise the sum of these $\chi^2$ terms.

For jets, the reconstructed direction in $\eta$ and $\phi$ is 
assumed to be measured accurately in comparison with their energy.
Therefore only their energy is varied in the fit. In addition, we assume
that uncertainties in the energy measurement directly translate to
uncertainties in the momentum measurement, and therefore $\vec{\beta} = \vec{p}/E$ is
also kept constant.

Before the fit, the mass constraint gives:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_prefit}
m_{\PHiggslight}^2 &= E_{\PHiggslight}^2 - \vec{p_{\PHiggslight}}^2 = (E_{\text{j} 1}+E_{\text{j} 2})^2 - (\vec{p_{\text{j} 1}} + \vec{p_{\text{j} 2}})^2 \notag\\
& = 2E_{\text{j} 1}E_{\text{j} 2} + m_{\text{j} 1}^2 +m_{\text{j} 2}^2 - 2\vec{p_{\text{j} 1}}\vec{p_{\text{j} 2}} \notag\\
& = m_{\text{j} 1}^2 +m_{\text{j} 2}^2 - 2E_{\text{j} 1}E_{\text{j} 2}(1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}})\notag\\
&\Rightarrow (1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}}) = \frac{m_{\PHiggslight}^2 - m_{\text{j} 1}^2 - m_{\text{j} 2}^2}{2E_{\text{j} 1}E_{\text{j} 2}}.
\end{align}
When varying the energy of the first jet in the fit, equation \ref{eqn:kinfit_prefit} can be 
rewritten to derive an expression for the updated energy of the second jet. Using $\mathcal{A} = (1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}})$ 
and
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:gamma_def}
\gamma = \frac{1}{1-\beta^2} \Rightarrow \gamma^2 = \frac{1}{1-\beta^2} = \frac{1}{1-p^2/E^2} = \frac{E^2}{m^2},
\end{equation}
we get:
~\vspace{-0.5\baselineskip}
\begin{align}\label{eqn:kinfit_variation}
m_{\PHiggslight}^2 &= m_{\text{j} 1}^2 + m_{\text{j} 2}^2 - 2E_{\text{j} 1}E_{\text{j} 2}(1-\vec{\beta_{\text{j} 1}}\vec{\beta_{\text{j} 2}})\notag\\
&= m_{\text{j} 1}^2 +\frac{E_{\text{j} 2,\text{fit}}^2}{\gamma_{\text{j} 2}^2} +2\mathcal{A}E_{\text{j} 1}E_{\text{j} 2,\text{fit}}\notag\\
\Rightarrow E_{\text{j} 2}^{\text{fit}}& = \frac{(-2E_{\text{j} 1}\mathcal{A} + \sqrt{4E_{\text{j} 1}^2\mathcal{A} - 4(m_{\text{j} 1}^2-m_{\PHiggslight}^2)\gamma_{\text{j} 2}^{-2}})\gamma_{\text{j} 2}^2}{2}\notag\\
&= - E_{\text{j} 1}\mathcal{A}\gamma_{\text{j} 2}^2+\sqrt{E_{\text{j} 1}^2\mathcal{A}\gamma_{\text{j} 2}^4 - (m_{\text{j} 1}^2 - m_{\PHiggslight}^2)\gamma_{\text{j} 2}^2}\notag\\
&\Rightarrow E_{\text{j} 2}^{\text{fit}} = E_{\text{j} 1}\mathcal{A}\gamma_{\text{j} 2}^2(-1 + \sqrt{1+\frac{m_{\PHiggslight}^2 - m_{\text{j} 1}^2}{E_{\text{j} 1}^2\mathcal{A}\gamma_{\text{j} 2}^2}}).
\end{align}

The fitting procedure additionally modifies the masses of the jets as 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{\text{j}_{1,2}}^{\text{fit}} = m_{\text{j}{1,2}}\frac{E_{\text{j}{1,2}}^{\text{fit}}}{E_{\text{j}{1,2}}}.
\end{equation}
The $\chi^2$ term for each jet is calculated as $\chi_{\text{j} 1,2}^2 = \frac{E_{\text{j} 1,2}^{\text{fit}}-E_{\text{j} 1,2}^{\text{meas}}}{\sigma_{\text{j} 1,2}}$, where `meas' denotes the measured value and `fit' the value given by the fit.

For taus only the visible decay products are measured. Assuming these point in 
the same direction as the original tau, a similar procedure as for the jets can be employed to constrain the energy of the second tau
when varying the energy of the first tau in the fit. The masses of the taus are kept fixed at $m_{\Pgt}$ throughout the procedure.

@@

The measured recoil is 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilmeas}
\vec{p}_{\text{T,recoil}}^{\text{ meas}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ meas}} = -\vec{p}_{\text{T,miss}}^{\text{ meas}} - \vec{p}_{\text{T},\text{j} 1}^{\text{ meas}} - \vec{p}_{\text{T},\text{j} 2}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_1^{\text{vis}}}^{\text{ meas}} - \vec{p}_{\text{T},\Pgt_2^{\text{vis}}}^{\text{ meas}},
\end{equation}
and the recoil from the fit is,
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilfit}
\vec{p}_{\text{T,recoil}}^{\text{ fit}} = -\vec{p}_{\text{T,\PHiggs}}^{\text{ fit}} = - \vec{p}_{\text{T},\text{j} 1}^{\text{ fit}} - \vec{p}_{\text{T},\text{j} 2}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_1}^{\text{ fit}} - \vec{p}_{\text{T},\Pgt_2}^{\text{ fit}}.
\end{equation}
A $\chi^2$ corresponding to the agreement between the fitted and measured recoil is reconstructed as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_recoilchi2}
\chi^2_{\text{recoil}} = (\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}})^T V_{\text{recoil}}^{-1}(\vec{p}_{\text{T,recoil}}^{\text{ fit}} - \vec{p}_{\text{T,recoil}}^{\text{ meas}}),
\end{equation}
where the covariance matrix $V_{\text{recoil}}$ of the recoil vector is estimated as 
\begin{equation}\label{eqn:kinfit_recoilcov}
V_{\text{recoil}} = V_{\vec{p}_{\text{T,miss}}} - V_{\text{j} {1}} - V_{\text{j} 2},
\end{equation}
 from the covariance matrices of the jets and
the covariance matrix of the missing transverse momentum. The latter is estimated in the process of determining the MVA \MET,
while the covariance matrices of the jets can be written in terms of the position, momentum, and energy resolution of the jets. 
The total $\chi^2$ term that needs to be minimised in the fit can then be written as
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_chitot}
\chi^2 = \chi^2_{\text{j} 1} + \chi^2_{\text{j} 2} + \chi^2_{\text{recoil}}.
\end{equation}
The results of the kinematic fit are the tau and jet four-vectors with their energies and momenta
set to the best fit values found for them in the fit. These can then be added together to find
the mass of the heavy Higgs boson as reconstructed by the kinematic fit.

As illustrated in figure \ref{fig:kinfitvsmjj}a the use of the kinematic fit greatly
improves the resolution of the reconstructed heavy Higgs boson mass in signal events, when 
compared with the simple four-body mass reconstruction. It also shifts the mean of the
distribution closer to the true value. It is also insightful to make such a comparison
for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
shown in figure \ref{fig:Hhh_selection_masscuts}. This comparison between four-body mass and
kinematic fit mass for \ttbar events is shown in figure 
\ref{fig:kinfitvsmjj}b. This figure shows that the mass distribution for
background events is less affected by the kinematic fit, although due to the
invariant mass constraint the minimum of the reconstructed mass distribution
is forced to $250\,\GeV$.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. The yield of
\Ztautau in each category is evaluated in two steps. In the first
step the total yield after the initial event selection, before subdividing into categories,
is evaluated in the simulated \Ztautau sample. In the second step the yield obtained 
in the first step is scaled by the efficiency with which such events pass the 
category selection in the embedded sample.
The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
The \ttbar shape and normalisation are both estimated using simulation.
%Both the \ttbar shape and normalisation are estimated using simulation.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
The resulting scale factor is $1.033 \pm 0.013\text{ (stat.)}\pm 0.088\text{ (syst.)}$. The
statistical and systematic uncertainties are added in quadrature to give a 9\% uncertainty,
which is applied to the \ttbar process.

\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to \mbox{low-\mT}~extrapolation
 factor is determined from the \Wjets simulation.
The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

@@

The shapes in all categories are taken from same-sign data with the electron or muon
isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
inverting the light lepton isolation requirements, the category definition
is relaxed to obtain the shapes. For the purposes of QCD shape
estimation, jets are considered b-tagged if they pass the loose b-tagging
working point.
\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shapes and normalisations are
estimated using simulated samples. Dedicated $\Pe\rightarrow\Pgth$
fake rate corrections, described in section \ref{sec:hhh_datamc}, are
applied to adjust the \Zee normalisation. The $\Pgm\rightarrow\Pgth$ 
fake rate correction was found to be close to 1 and therefore the \Zmm
normalisation is not subject to such an additional correction factor.

@@

shape of the kinematic fit mass distribution. 

@@

fake rate correction is close \mbox{to 1,} which is why it is not applied, but the uncertainty is 

@@

\item \ttbar: The uncertainty in the measured \ttbar scale factor 9\%. 
